### 2022-03-20 CV2/CV.tex
new cv

\documentclass[a4paper,10pt]{article} % Default font size and paper size
\usepackage{fontspec} % For loading fonts
\setmainfont{[Fontin-Regular.otf]}
\defaultfontfeatures{Mapping=tex-text}
% \setmainfont{[Fontin-Regular.otf]} % Main document font
% \setmainfont[SmallCapsFont = Fontin-SmallCaps.otf]{[Fontin-Regular.otf]} % Main document font
\setmainfont{Fontin-Regular.otf}[
BoldFont       = Fontin-Bold.otf ,
ItalicFont     = Fontin-Italic.otf ,
SmallCapsFont  = Fontin-SmallCaps.otf ]

@@

\begin{tabular}{rl}
\textsc{Phone:} & +7 905 719 06 98\\
\textsc{Email:} & \href{mailto:dakovalev1@gmail.com}{dakovalev1@gmail.com}\\
\textsc{Website:} & \href{https://www.dmitry-kovalev.com}{www.dmitry-kovalev.com}\\
\textsc{Google Scholar:} &\href{https://scholar.google.com/citations?user=qHFA5z4AAAAJ}{https://scholar.google.com/citations?user=qHFA5z4AAAAJ}
\end{tabular}

@@

\section{Education}

\begin{tabular}{rl}	
\textsc{2014-2018}& BS in Applied Mathematics and Physics\\
& \textbf{Moscow Institute of Physics and Technology}, Dolgoprudny, Russia\\
& Advisor: \href{https://scholar.google.com/citations?user=AmeE8qkAAAAJ}{Alexander Gasnikov}\\
&\\
\textsc{2018-2019}& MS in Computer Science\\
& \textbf{King Abdullah University of Science and Technology}, Thuwal, Saudi Arabia\\
& Advisor: \href{https://richtarik.org}{Peter Richt\'{a}rik}\\
&\\
\textsc{2018-2021}& MS in Applied Mathematics and Physics\\
& \textbf{Moscow Institute of Physics and Technology}, Dolgoprudny, Russia\\
& Advisor: \href{https://scholar.google.com/citations?user=AmeE8qkAAAAJ}{Alexander Gasnikov}\\
&\\
\textsc{2019-Now}& PhD in Computer Science\\
& \textbf{King Abdullah University of Science and Technology}, Thuwal, Saudi Arabia\\
& Advisor: \href{https://richtarik.org}{Peter Richt\'{a}rik}\\
\end{tabular}

@@

\section{Awards}

%\begin{itemize}
%	\item \textbf{CEMSE Research Excellence Award}, King Abdullah University of Science and Technology, 2021
%	
%	\item \textbf{Best Student Paper Award}, International Workshop on Federated Learning for User Privacy and Data Confidentiality in Conjunction with ICML 2021 (FL-ICML'21)
%\end{itemize}
%
%
%
%
%
%\textbf{Ilya Segalovich Scientific Prize}, Yandex, 2021
%
%\textbf{Ilya Segalovich Scientific Prize}, Yandex, 2020

\begin{tabular}{cl}
	\textsc{2021} & \textbf{CEMSE Research Excellence Award}, King Abdullah University of Science and Technology\\
	\textsc{2021} & \textbf{Best Student Paper Award}, FL-ICML 2021 Workshop\\
	\textsc{2021} & \textbf{Ilya Segalovich Scientific Prize}, Yandex \\
	\textsc{2020} & \textbf{Ilya Segalovich Scientific Prize}, Yandex\\
	\textsc{2015-2017} & \textbf{Abramov’s Fund Scholarship}, Moscow Institute of Physics and Technology\\
	\textsc{2014} & \textbf{Asian Physics Olympiad (APhO), Honourable Mention}, Singapore\\
	\textsc{2014} & \textbf{All-Russian School Physics Olympiad, Final Round Prize-Winner}, Saint-Petersburg\\
	\textsc{2014} & \textbf{All-Russian School Programming Olympiad, Region Round Winner}, Moscow\\
	\textsc{2014} & \textbf{All-Russian School Math Olympiad, Region Round Winner}, Moscow\\
	\textsc{2012-2014} & \textbf{Russian President’s Scholarship for High School Sudents}\\
	\textsc{2012-2014} & \textbf{Moscow Governor’s Scholarship for High School Sudents}\\
	\textsc{2013} & \textbf{All-Russian School Physics Olympiad, Final Round Winner}, Vladivostok\\
	\textsc{2012} & \textbf{All-Russian School Physics Olympiad, Final Round Prize-Winner}, Saransk\\
\end{tabular}

%----------------------------------------------------------------------------------------

% \newpage

% %----------------------------------------------------------------------------------------
% %	GRADE TABLES
% %----------------------------------------------------------------------------------------

% \par{\centering\Large \hypertarget{grds}{Master of Science in \textsc{Finance}}\par}\large{\centering Grades\par}\normalsize

% \begin{center}
% \begin{tabular}{lcc}
% \multicolumn{1}{c}{\textsc{Exam}} & \textsc{Grade}&\textsc{Credit Hrs}\\ \hline
% Corporate Finance (Valuation) & 25 & 6\\
% Financial Statement Analysis & 28 & 6\\
% Statistics & 27 & 6\\
% Theory of Finance & 26 & 6\\
% Quantitative Methods for Finance & 30 & 6\\
% Econometrics & 24 & 6\\
% Derivatives & 31 & 6\\
% Management of Financial and Insurance Companies & 30 & 6\\
% Business Law & 31 & 6\\
% Investment Banking	& 28 & 6\\ \\		
% Behavioral Models for Economics and Finance	 & 29 & 6\\
% Numerical Methods for Finance & 29 & 6\\
% Advanced Derivatives & 30 & 6\\
% Fixed Income (Advanced Methods) & 30 & 6\\ \\
% English Language & 30 &	4\\
% French Language & 31 &	4\\	
% Internship & & 8\\		
% Final Thesis & & 20\\	
% & Total & 120\\\cline{2-3}
% &\textsc{Gpa}&\textbf{8.0}
% \end{tabular}
% \end{center}
% \bigskip
% \hrule
% \bigskip

% %------------------------------------------------

% \bigskip

% \par{\centering\Large \hypertarget{grds_usc}{Exchange Program at \textsc{usc}, Los Angeles}\par}\large{\centering Grades\par}\normalsize

% \begin{center}
% \begin{tabular}{lcc}
% \multicolumn{1}{c}{\textsc{Exam}} & \textsc{Grade} & \textsc{Grade Points}\\ 
% \hline
% Corporate Financial Strategy & A & 4\\
% Derivatives & A & 4\\
% Money, Credit, and Banking & A & 4\\
% Business Strategy & A- & 3.5\\
% & &\\\cline{2-3}
% & \textsc{Gpa} & \textbf{3.875}
% \end{tabular}
% \end{center}

% %----------------------------------------------------------------------------------------

>>>>

\documentclass[a4paper,10pt]{article} % Default font size and paper size
%\usepackage[T1]{fontenc}
%\usepackage[utf8]{inputenc}
\usepackage{fontspec} % For loading fonts

%\setmainfont{[Fontin-Regular.otf]}
\defaultfontfeatures{Mapping=tex-text}
% \setmainfont{[Fontin-Regular.otf]} % Main document font
% \setmainfont[SmallCapsFont = Fontin-SmallCaps.otf]{[Fontin-Regular.otf]} % Main document font
\setmainfont{Fontin-Regular.otf}[
BoldFont       = Fontin-Bold.otf ,
ItalicFont     = Fontin-Italic.otf ,
SmallCapsFont  = Fontin-SmallCaps.otf ]

@@

\begin{tabular}{rl}
\textsc{Email} & \href{mailto:dakovalev1@gmail.com}{dakovalev1@gmail.com}\\
\textsc{Website} & \href{https://www.dmitry-kovalev.com}{www.dmitry-kovalev.com}\\
\textsc{Phone} & +7 905 719 06 98\\
\textsc{Google Scholar} &\href{https://scholar.google.com/citations?user=qHFA5z4AAAAJ}{https://scholar.google.com/citations?user=qHFA5z4AAAAJ}
\end{tabular}

@@

\section{Education}
\begin{tabular}{rl}	
\textsc{2014-2018}& BS in Applied Mathematics and Physics\\
& \textbf{Moscow Institute of Physics and Technology}, Dolgoprudny, Russia\\
& Advisor: \href{https://scholar.google.com/citations?user=AmeE8qkAAAAJ}{Alexander Gasnikov}\\
\textsc{2018-2019}& MS in Computer Science\\
& \textbf{King Abdullah University of Science and Technology}, Thuwal, Saudi Arabia\\
& Advisor: \href{https://richtarik.org}{Peter Richt\'{a}rik}\\
\textsc{2018-2021}& MS in Applied Mathematics and Physics\\
& \textbf{Moscow Institute of Physics and Technology}, Dolgoprudny, Russia\\
& Advisor: \href{https://scholar.google.com/citations?user=AmeE8qkAAAAJ}{Alexander Gasnikov}\\
\textsc{2019-Now}& PhD in Computer Science\\
& \textbf{King Abdullah University of Science and Technology}, Thuwal, Saudi Arabia\\
& Advisor: \href{https://richtarik.org}{Peter Richt\'{a}rik}\\
\end{tabular}

\section{Research Interests}
 Optimization Algorithms, Distributed Optimization, Machine Learning,

@@

\section{Awards}
\hypersetup{colorlinks,breaklinks,urlcolor=black,linkcolor=black}
\begin{tabular}{cl}
	\textsc{2021} & \textbf{CEMSE Research Excellence Award}, King Abdullah University of Science and Technology\\
	\textsc{2021} & \href{http://federated-learning.org/fl-icml-2021/}{\textbf{Best Student Paper Award}, FL-ICML 2021 Workshop}\\
	\textsc{2021} & \href{https://yandex.ru/scholarships/scholars}{\textbf{Ilya Segalovich Scientific Prize}, Yandex} \\
	\textsc{2020} & \href{https://yandex.ru/scholarships/scholars}{\textbf{Ilya Segalovich Scientific Prize}, Yandex}\\
	\textsc{2015-2017} & \textbf{Abramov’s Fund Scholarship}, Moscow Institute of Physics and Technology\\
	\textsc{2014} & \textbf{Asian Physics Olympiad (APhO), Honourable Mention}, Singapore\\
	\textsc{2014} & \textbf{All-Russian School Physics Olympiad, Final Round Prize-Winner}, Saint-Petersburg\\
	\textsc{2014} & \textbf{All-Russian School Programming Olympiad, Region Round Winner}, Moscow\\
	\textsc{2014} & \textbf{All-Russian School Math Olympiad, Region Round Winner}, Moscow\\
	\textsc{2012-2014} & \textbf{Russian President’s Scholarship for High School Sudents}\\
	\textsc{2012-2014} & \textbf{Moscow Governor’s Scholarship for High School Sudents}\\
	\textsc{2013} & \textbf{All-Russian School Physics Olympiad, Final Round Winner}, Vladivostok\\
	\textsc{2012} & \textbf{All-Russian School Physics Olympiad, Final Round Prize-Winner}, Saransk\\
\end{tabular}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}

\newpage

\section{Papers}

\input{papers.tex}
